The Right Way to Search Evolving Graphs

### 2016-01-28 paper.tex
update abstract

\begin{abstract}
We present a correctly verified breadth first search (BFS) algorithm for evolving graphs. Using simple examples, we show na\"ive matrix-matrix multiplication on time-dependent adjacency matrices miscounts the number of temporal paths and therefore should be avoided if temporal path is a component of the algorithm. We formulate our
evolving graph BFS using the language of linear algebra and present an adjacency matrix representation of the equivalent static graph, which is used to study
interesting properties about the original evolving graphs. 
% We generalize the breadth first search (BFS) algorithm to evolving graphs and
% prove its correctness.
% The BFS generates paths with nontrivial structure, which we term temporal paths.
% We also show with simple counterexamples that products of adjacency matrices alone
% do not have the correct combinatorics of enumerating temporal paths.
% Generalizing BFS to evolving graphs requires careful tracking of active nodes
% which participate in the definition of edges at specific times.
% We discuss how the structure of temporal paths is reflected in adjacency matrix
% representations of evolving graphs,
% as well as implications for real world applications such as the analysis of citation networks.
\end{abstract}

>>>>

\begin{abstract}
Evolving graphs arise in many different contexts where the 
interrelations between data elements change over time. 
We present a breadth first search (BFS) algorithm for evolving graphs
that can track (active) nodes correctly. 
Using simple examples, we show na\"ive matrix-matrix multiplication on time-dependent adjacency matrices miscounts the number of temporal paths. 
By mapping an evolving graph to an adjacency matrix of the equivalent static graph, 
we  prove the properties of the BFS algorithm using the properties of the 
adjacency matrix.
We show an application of our algorithm in mining citation networks.

% We generalize the breadth first search (BFS) algorithm to evolving graphs and
% prove its correctness.
% The BFS generates paths with nontrivial structure, which we term temporal paths.
% We also show with simple counterexamples that products of adjacency matrices alone
% do not have the correct combinatorics of enumerating temporal paths.
% Generalizing BFS to evolving graphs requires careful tracking of active nodes
% which participate in the definition of edges at specific times.
% We discuss how the structure of temporal paths is reflected in adjacency matrix
% representations of evolving graphs,
% as well as implications for real world applications such as the analysis of citation networks.
\end{abstract}
